Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-31 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:31	21:58:12	(Mon31.Aug)

While MVDR is free to choose non-symmetric windows, we can observe from \Fig{mvdr_selected_windows} that it prefers symmetric ones. In shadow and speckle the windows are fully symmetric, while in highlight the windows are approximately symmetric within the opening angle of the sonar. The peak sidelobe levels are between that of the rectangular and Hamming window. This correspond to Kaiser windows with $\beta$-values of 0 and 2, respectively.

@@

Unlike the method described by Synne\aa{}g~\cite{Synnevag2008} we do not let LCA choose from  inverted Kaiser windows. These have a spatial response with mainlobe width narrower than that of a rectangular window, but at the expense of drastically increased white noise gain. We have found that these windows hardly ever get used on experimental data, in particular steered versions which ever worsened white noise gain. We can infer the same from \Fig{mvdr_selected_windows} by noting that the maximum sidelobe level rarely exceeds the rectangular window level of -13\;dB.

>>>>

While MVDR is free to choose non-symmetric windows, we can observe from \Fig{mvdr_selected_windows} that it prefers symmetric ones. In shadow and speckle the windows are fully symmetric, while in highlight the windows are approximately symmetric within the opening angle of the sonar. The peak sidelobe levels are between that of the rectangular and Hamming window. This corresponds to Kaiser windows with $\beta$-values of 0 and 2, respectively.

@@

Unlike the method described by Synnev\aa{}g~\cite{Synnevag2008} we do not let LCA choose from  inverted Kaiser windows. These have a spatial response with mainlobe width narrower than that of a rectangular window, but at the expense of drastically increased white noise gain. We have found that these windows hardly ever get used on experimental data, in particular steered versions which ever worsened white noise gain. We can infer the same from \Fig{mvdr_selected_windows} by noting that the maximum sidelobe level rarely exceeds the rectangular window level of -13\;dB.
